A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels

### 2018-05-14 article MDPI/hill et al 2018.tex
update 14_05_2018
update 14_05_2018

With the objective of extending the use of the German NFI data to additional estimation on small scale management levels, we evaluated the performance of design-based small area regression estimators with respect to their suitability for future operational large scale application. For this reason, we conducted a case study in the German federal state of Rhineland-Palatinate where we applied the SRS, the \psmall{} and the \extpsynth{} estimators to produce estimates of the mean timber volume on two forest management levels over the entire federal state area, comprising 45 and 405 small area units respectively. In order to assess and compare the performance of the estimators, it was of particular interest to gather information about the magnitudes of estimation precision they can provide.\par

%Important criteria were considered to be:
%
%- the magnitude of estimation precision on the respective management level
%- the ability of the small area estimators to be
%   a) applied for large scale application, and 
%   b) frequently repeated
%   c) transferred / applicable to numerous forest attributes under comparable low effort
%- the identification of suitable auxiliary information, especially remote sensing data, with respect to their predictive power and their future availability

>>>>

With the objective of extending the use of the German NFI data to additional estimation on small-scale management levels, we evaluated the performance of design-based small area regression estimators with respect to their suitability for future operational large scale application. For this reason, we conducted a case study in the German federal state of Rhineland-Palatinate where we applied the SRS, the \psmall{} and the \extpsynth{} estimators to produce estimates of the mean timber volume on two forest management levels over the entire federal state area, comprising 45 and 405 small area units respectively. In order to assess and compare the performance of the estimators, it was of particular interest to gather information about the magnitudes of estimation precision they can provide.\par

%Important criteria were considered to be:
%
%- the magnitude of estimation precision on the respective management level
%- the ability of the small area estimators to
%   a) be applied for large scale application, and 
%   b) be frequently repeated
%   c) be transferred / applicable to numerous forest attributes under comparable low effort
%   d) provide reliable specification of their estimation errors (uncertainties / precisions)
%- the identification of suitable auxiliary information, especially remote sensing data, with respect to their predictive power and their future availability
